Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-19 paper/paper.tex
Updates to WA-DPDS

DPDS algorithm does not use any information about workflow structure: it deals
only with scheduling of individual released/ready tasks using their
workflow priorities. If there are no high priority tasks in the ready queue,
then lower priority tasks are submitted to idle resources. This may lead to the
deficiency in the following scenario: if a long-running task of low
priority is submitted to the idle machine and then several high
priority tasks are released to the ready queue, they become delayed by the
execution of the low priority task. This usually does not cause a problem when
the number of tasks and resources is high, but when the execution approaches the
budget and deadline constraint, we have observed that tasks of low-priority
workflows may prevent higher priority workflows from completion. This
observation leads to the improved algorithm which we call Workflow-Aware DPDS
(WA-DPDS).

WA-DPDS extends DPDS by introducing a workflow admission procedure, which is
invoked each time a task of a new workflow is at the head of priority queue,
i.e. just before it is submitted. The procedure estimates if there is enough
budget remaining to admit a new workflow: if not, all its tasks are rejected.
Algorithm~\ref{alg:wa-dpds} estimates the cost of admitting a new workflow and
compares it to the current cost (consumed budget) and remaining budget, taking
into account that started VMs have been already paid for. It adds a small safety
margin choosen to avoid overestimation of a budget.

>>>>

The DPDS algorithm does not use any information about the structure of the workflows
in the ensemble when scheduling tasks: it looks only at the priorities of the ready 
tasks when deciding which task to schedule next. It does not consider whether a lower 
priority task belongs to a workflow that it will never be able to complete given the 
current budget and deadline. As a result, DPDS may execute lower priority tasks just 
to keep VMs busy that will end up delaying higher priority tasks, making it less likely
that higher priority workflows will be able to finish.

In order to address this issue, the Workflow-Aware DPDS (WA-DPDS) algorithm extends 
DPDS by introducing a workflow admission procedure. The admission procedure is
invoked whenever WA-DPDS sees the first task of a new workflow at the head of the 
priority queue (i.e. no other tasks from that workflow have been scheduled yet). 
The procedure estimates if there is enough
budget remaining to admit the new workflow: if not, all its tasks are rejected.
Algorithm~\ref{alg:wa-dpds} estimates the cost of admitting a new workflow and
compares it to the current cost (consumed budget) and remaining budget, taking
into account that started VMs have been already paid for. It adds a small safety
margin choosen to avoid overestimation of a budget.
